Supplementary Appendix: Trends in the contribution of major causes of death to the black-white life expectancy gap by US state. A retrospective study of all deaths between 1969 and 2013

### 2018-03-23 Manuscript/Appendix-agestd-mort-rates.Rmd

This is the supplementary appendix for the paper, "Trendfs in the contribution of major causes of death to the black-white life expectancy gap by US state. A retrospective study of all deaths between 1969 and 2013."

Corinne A Riddell, PhD; Kathryn T Morrison, PhD; Sam Harper, PhD; Jay S Kaufman, PhD

>>>>

This is the supplementary appendix for the paper, "Trends in the contribution of major causes of death to the black-white life expectancy gap by US state. A retrospective study of all deaths between 1969 and 2013."

Corinne A Riddell, PhD; Kathryn T Morrison, PhD; Jay S Kaufman, PhD; Sam Harper, PhD;
